---
title: "Rpopulartimes"
author: "Christian Barz"
date: "created:2021-07-28, reviewed: `r lubridate::today()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# get popular times using google API

populartimes is an R translation of the python library [populartimes](https://github.com/m-wrzr/populartimes). It provides access to [Google Places API](https://developers.google.com/maps/documentation/places/web-service/overview).

The API uses Google Places Web Service and each APi call is priced over a monthly budget.

For legal concerns please read [Issue #90](https://github.com/m-wrzr/populartimes/issues/90).

As Google Maps is constantly updated this library can be unstable.

## get started and setup

- install the library
```
install.packages("remotes")
remotes::install_github("JosiahParry/populartimes")
```
- [get Google Map API key](https://developers.google.com/places/web-service/get-api-key)
  - create a project with a billing account and the Places API enabled, i.e.
  - [create google cloud project](https://console.cloud.google.com/projectcreate?_ga=2.109071308.870652759.1627453303-208296733.1627165040) 
  - [create API key](https://developers.google.com/maps/documentation/places/web-service/get-api-key?hl=de)
  - utilize API key, for example by setting an environment variable `Google_key` to your key value. For example `Sys.setenv("GOOGLE_KEY" = "your-key-value")`
  
  
```{r}
library(populartimes)
library(tidyverse)
```

## Test
  
```{r}
test <- poptimes_from_address("Brennerberg", "Tiroler Str. 33, 13187 Berlin")
test
```

## define places of interest

```{r}
places_of_interest <- tibble(
  location = c("Brennerberg",
               "Kinderspielplatz Arnimplatz",
               "Zukunftswerkstatt Heinersdorf",
               "Kissingen-Stadion",
               "Diseño",
               "U Vinetastr.",
               "S+U Pankow",
               "Wochenmarkt Pankow",
               "Kirschblüten Pfad",
               "REWE", # Rewe Eschengraben
               "Neumann Forum",
               "S Pankow-Heinersdorf",
               "PENNY" # Sotty
               ),
  address = c("Tiroler Str. 33, 13187 Berlin",
             "Prenzlauer Berg, 10439 Berlin",
             "Romain-Rolland-Straße 112, 13089 Berlin",
             "Forchheimer Str. 22, 13189 Berlin",
             "Berliner Str. 53, 13189 Berlin",
             "13189 Berlin",
             "13187 Berlin",
             "Breite Str. 17, 13187 Berlin",
             "KGA Bornholm I 1, 10439 Berlin",
             "Eschengraben 47, 13189 Berlin",
             "Neumannstraße 13, 13189 Berlin",
             "13187 Berlin",
             "Wisbyer Str. 38, 13189 Berlin"
             ),
  place_ID = c("ChIJP9zn9BFSqEcRE2ymZMvoRhk",
               "ChIJrYEFFAVSqEcRljVmHYbNz54",# arnimplatz
               "ChIJlcwYIIZNqEcRwLIXc78_Bx8",
               "ChIJ8UJqZXRSqEcR20TKVGLZY3U",# kissingen stadion
               "ChIJByIw1g1SqEcRaiSAcRwgBdk",
               "ChIJvXXwxQ1SqEcRuURoh0MQACM",# U Vineta
               "ChIJgVQMmG1SqEcROB59hvVm9K0",
               "ChIJeSaL2mtSqEcR8K5fSNo-tUM",#wochenmarkt pankow
               "ChIJUwlQieFTqEcRn80wbzLNLM4",
               "ChIJDWbXAvZNqEcRJ0KxM9Uo3lA",# REWE eschengraben
               "ChIJ3XM6HAtSqEcR2Or9CGbkI2E",# neumannforum
               "ChIJqVSMNHlSqEcRODE2mEx0GwI",
               "ChIJn_rebfdNqEcR0pIqK93_hW0"# konsum Sotty
               )
  )

#Edeka neumannstr, 
#der rewe Eschengraben, 

places_of_interest
```

get popular times of locations

```{r}
locations <- places_of_interest$location
pop_times <- lapply(locations, function(x){
  address <- places_of_interest %>%
    filter(location == x) %>%
    pull(address)
  poptimes_from_address(place_name = x,
                        address = address)
}
) %>%
  purrr::set_names(locations)
```


## prepare and save data for app

convert list to data frame

```{r}
pop_times_df <- lapply(locations, function(x){
  df <- pop_times[[x]] 
  dt <- df$popular_times[[1]]
  dt <- dt %>%
    mutate(lon = df$lon,
           lat = df$lat,
           time_spendt = df$time_spent,
           current_pop = df$current_popularity,
           location = x
           )
  return(dt)
}) %>%
  purrr::reduce(rbind) %>%
  inner_join(x = ., y = places_of_interest) %>%
  select(-place_ID)
```

convert `day_of_week` from a numerical value to a string

```{r}
pop_times_df <- pop_times_df %>%
  mutate(day_of_week = if_else(day_of_week=="1","Sonntag", day_of_week),
         day_of_week = if_else(day_of_week=="2","Montag", day_of_week),
         day_of_week = if_else(day_of_week=="3","Dienstag", day_of_week),
         day_of_week = if_else(day_of_week=="4","Mittwoch", day_of_week),
         day_of_week = if_else(day_of_week=="5","Donnerstag", day_of_week),
         day_of_week = if_else(day_of_week=="6","Freitag", day_of_week),
         day_of_week = if_else(day_of_week=="7","Samstag", day_of_week),
         )
pop_times_df %>% head()
```

pivot the data

```{r}
pop_times_df_pivot <- pop_times_df %>%
  select(-lat,-lon,-current_pop) %>%
  pivot_wider(names_from = day_of_week, 
              id_cols = c(hour,location),
              values_from = popularity) %>%
  inner_join(x =., y = places_of_interest %>% select(-place_ID))

pop_times_df_pivot %>% head()
```

```{r eval=FALSE}
write_csv(pop_times_df, 
          "./data/pop_times.csv",
          )

write_csv(pop_times_df_pivot, 
          "./data/pop_times_pivot.csv",
          )
```


## analysis

get top 3 times per place

```{r}
pop_times_df %>%
  arrange(desc(popularity)) %>%
  group_by(location) %>%
  slice(1:3)
```


```{r}
plots <- lapply(locations, function(x){
  pop_times_df %>%
  filter(location == x) %>%
  ggplot(aes(x = hour, y = popularity,
             colour = factor(day_of_week))) + geom_point() + labs(title = paste("location:", x))
})
plots
```



